Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-10-01 ms.tex
updated the long time series through all CV3 data

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{plot_mmm.pdf}
\caption{Time Series plot through the CV3 photometric stability campaign.
All test shown above were using the Weak Lens +8 mode, with a PSF as shown in Figure \ref{fig:WLP8PSF}.
13 tests (FULL1 through FULLQ) are all in full frame mode, while WLP8SUB used a 320$\times$320 subarray and WLP8SUB640 used a 640$\times$640 subarray.
The WLP8SUB showed the smallest standard deviation of any testof any NIRCam mode explored.}\label{fig:CV3longTser}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.79\columnwidth]{plot_mmm.pdf}
\caption{Time Series plot through the CV3 photometric stability campaign.
All test shown above were using the Weak Lens +8 mode, with a PSF as shown in Figure \ref{fig:WLP8PSF}.
13 tests (FULL1 through FULL6) are all in full frame mode, while SUB used a 320$\times$320 subarray and SUB640 used a 640$\times$640 subarray.
The WLP8SUB showed smaller standard deviation that the full frame tests, when the linear trend is removed.}\label{fig:CV3longTser}
\end{figure}
